---
title: "Introduction"
author: "Timo Roest"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>"
)
source("~/.Rprofile")
library(ghmapper)
library(tidyverse)
library(httr)
library(leaflet)
library(sp)
library(jsonlite)
library(maptools)
```

To provide a quick introduction to the way this library works, this vignette will plot several routes that are found using the graphhopper API. 

## API Key

One initial aspect is that in order to use the GH API, you will need an API key. This can be requested on their website, and licences can be purchased. A personal use one is available. 

In order to use this immediately within the library, you can set it as shown below:

```{r load_key, eval=FALSE, include=TRUE}
options("Graphhopper_key" = "[PUT YOUR KEY HERE]")
```

If you have not set this KEY, you will be prompted the first time you run the `gh_api` function.

## Download Data

The data is downloaded by providing start and end location as a string, in lat/long, seperated by commas, as shown below. 
Note that additional parameters can be set. More information can be found by typing `?gh_api`.

```{r download}
routes <- gh_route(Start = "51.509840,-0.134860", End = "51.384880,-2.361970")
routes %>% 
  glimpse
```


## Plot

To visualise the results, the following command can be used:

```{r plot, out.width= '100%'}
plot_routes(routes)
```


